---
title: "World Economic data"
author: "Benedetto Lo Cicero"
date: "16 Juli 2019"
output: slidy_presentation
---
***
## Basic economic datas

In this html presentation I want to show some economic facts  obtained from the economic freedom institute (https://www.fraserinstitute.org/).
***

```{r echo=FALSE, message=FALSE, warning=TRUE}
library(shiny)
library(shinyWidgets)
library(dplyr)
library(stringr)
library(janitor)
library(plotly)
library(zoo)
library(lubridate)
df <- read.csv2("./2018_EconomicFreedom.csv")
df <- df[,1:9]
#df <- df[df$Year==2016,]

colnames(df) <- str_remove_all(colnames(df),'X[:digit:][:punct:]{2}')
colnames(df) <- str_replace_all(colnames(df),'[:punct:]'," ")
colnames(df) <- str_replace_all(colnames(df),'   ',' and ')
colnames(df) <- gsub('\\s+', '', colnames(df))
df <- remove_empty(df, which = c("rows", "cols"))

Continents <- read.csv("~/GitHub/Coursera_DevelopingDataProducts/Rshine/myFirstShiny/Continents.txt")
Continents <- Continents[,c(3,6:8)]

df <- merge(df,Continents,by.x="ISOCode",by.y="alpha.3")
df$ISOCode <- df$ISOCode %>% as.factor()
df$Countries <- df$Countries %>% as.factor()
df$region <- df$region %>% as.factor()
df$sub.region <- df$sub.region %>% as.factor()

```
***
## the shiny application consits economic map plot of the last year report

I colour the country using their summary index as reference

```{r echo=FALSE, message=FALSE, warning=FALSE}
# specify some map projection/options


library(plotly)
p <- plot_geo(df, locationmode = 'world') %>% 
  add_trace(
    z = ~SUMMARYINDEX, locations = ~ISOCode,
    color = ~SUMMARYINDEX, colors = c("green","blue") 
  ) %>%
  colorbar(title = "Summary Index")

p

```

***
## the user can select the country to be plot and see the map of summary index
```{r echo=FALSE, message=FALSE, warning=FALSE}
pal <- c("red", "blue", "green")
choices_country <- unique(as.character(df$Countries))
input <- choices_country[1:4]
dataset <- df %>% filter(Countries==input) %>% group_by(Countries) %>% filter(Year==max(Year))

plot_geo(dataset, locationmode = 'world') %>% 
    add_trace(
      z = ~SUMMARYINDEX, locations = ~ISOCode,
      color = ~SUMMARYINDEX, colors = c("green","blue") 
    )
```

*** 
## in parallel he will get the plot of the summary index according to the reported years
```{r echo=FALSE, message=FALSE, warning=FALSE}

dataset <- df %>% filter(Countries==input) %>% group_by(Countries)

dataset %>% group_by(Countries) %>% 
  plot_ly(x = ~ Year ) %>% 
  add_lines(y = ~ SUMMARYINDEX , 
            color = ~ factor(Countries)) %>% 
  layout(xaxis=list(title = "Year"),
         yaxis=list(title = "Summary index"))

```

